---
title: "R??????????????????week4"
author: "minwen"
date: "October,5,2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
weather <- sample(c("sunny", "rainy"), size = 1)
weather
if (weather == "sunny"){
 print("Running outdoors!")
} else {
 print("Working out in the gym!")
}

weather <- sample(c("sunny", "rainy"), size = 1)
weather
if (weather == "sunny"){
 print("Running outdoors!")
 } else {
 print("Working out in the gym!")
 }
 
weather <- sample(c("sunny", "rainy"), size = 1)
weather
if (weather == "sunny"){
 print("Running outdoors!")
 } else {
 print("Working out in the gym!")
 }


weather <- sample(c("sunny", "rainy"), size = 1)
weather
[1] "sunny"
if (weather == "sunny"){
print("Running outdoors!")
} else {
print("Working out in the gym!")
}
for (month in month.name){
 print(month)
 }
 
i <- 1
while (i < 13){
 print(month.name[i])
 i <- i + 1
 }

weather <- sample(c("sunny", "cloudy", "drizzle", "showers", "storm"), size = 1)
weather
if (weather == "sunny"){
 print("Running outdoors!")
 } else if (weather == "cloudy"){
 print("Cycling!")
 } else if (weather == "drizzle") {
 print("Working out in the gym!")
 } else {
 print("Couch potato.")
 }

 weather <- sample(c("sunny", "cloudy", "drizzle", "showers", "storm"), size = 1)
 weather
if (weather == "sunny"){
 print("Running outdoors!")
 } else if (weather == "cloudy"){
 print("Cycling!")
 } else if (weather == "drizzle") {
 print("Working out in the gym!")
 } else {
 print("Couch potato.")
 }

flip_results <- c() # ?????????????????????????????????????????????????????????
coin <- c(TRUE, FALSE) # TRUE ????????????,FALSE ????????????
n_flips <- 1 # ??????????????????????????????
while (sum(flip_results) < 3){
 flip_results[n_flips] <- sample(coin, size = 1) # ?????????????????????????????????
 n_flips <- n_flips + 1 # ????????????????????????????????????
}
flip_results # ???????????????????????????
length(flip_results) # ?????????????????????
length(flip_results)

for (month in month.name){
 if (month == "April"){
 break
 } else {
 print(month)
 }
 }

#?????????
#1
week <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
for(s in week)
    print(s)
#2    
week <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
i <- 1
while (i < 8){
 print(week[i])
 i <- i + 1
 }
#3
week <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
for(s in week)
    if(s == "Monday"){
    }else if(s == "Tuesday"){
        next
    }else if(s == "Wednesday"){
        next
    }else if(s == "Thursday"){
        next
    }else if(s == "Friday"){
        next
    }else{
        print(s)
    }
    
#????????????
abs(-5)
abs(-5:-1)
abs("Hello")

sqrt(2)
sqrt(1:10)

ceiling(9.527)
nums <- sqrt(c(7, 17, 27, 37, 47))
nums
ceiling(nums)

floor(9.527)
nums <- sqrt(c(7, 17, 27, 37, 47))
nums
floor(nums)

round(9.527)
round(9.527, digits = 0)
round(9.527, digits = 1)
round(9.527, digits = 2)

exp(1)
exp(2)

log(exp(1))
log(exp(2))
log(exp(3))

log10(10)
log10(10^2)
log10(10^3)

toupper("Learn R the easy way")#????????????
tolower("Learn R the easy way")#????????????

my_char <- "Learn R the easy way"
substr(my_char, start = 1, stop = 5)
substr(my_char, start = 7, stop = 7)
substr(my_char, start = 9, stop = 11)
substr(my_char, start = 13, stop = 16)
substr(my_char, start = 18, stop = 20)

my_char <- c("Learn", "R", "the", "easy", "way")
grep(pattern = "Learn", my_char)
grep(pattern = "R", my_char)
grep(pattern = "the", my_char)
grep(pattern = "easy", my_char)
grep(pattern = "way", my_char)
grep(pattern = "xyz", my_char)

my_char <- c("Learn", "R", "the", "easy", "way")
grep(pattern = "learn", my_char)
integer(0)
grep(pattern = "learn", my_char, ignore.case = TRUE)

my_char <- c("Learn", "R", "the", "easy", "way")
sub(pattern = "easy", replacement = "effortless", my_char)
my_char <- c("Learn", "R", "the", "easy", "way")
sub(pattern = "EASY", replacement = "effortless", my_char)
sub(pattern = "EASY", replacement = "effortless", my_char, ignore.case = TRUE)

my_char <- "Learn R the easy way"
strsplit(my_char, split = " ") 
my_char <- "Learn,R,the,easy,way"
strsplit(my_char, split = ",") 

char_1 <- "Learn"
char_2 <- "R"
char_3 <- "the"
char_4 <- "easy"
char_5 <- "way"
paste(char_1, char_2, char_3, char_4, char_5)
paste(char_1, char_2, char_3, char_4, char_5, sep = ",")
paste(char_1, char_2, char_3, char_4, char_5, sep = "")

my_seq <- 1:5
mean(my_seq)
my_seq <- c(my_seq, NA) # ???????????? NA
mean(my_seq) # ????????? NA
mean(my_seq, na.rm = TRUE) # ???????????????

my_seq <- 1:5
sd(my_seq)
my_seq <- c(my_seq, NA) # ???????????? NA
sd(my_seq)
sd(my_seq, na.rm = TRUE) # ???????????????

my_seq <- 1:5
median(my_seq)
my_seq <- c(my_seq, NA) # ???????????? NA
median(my_seq)
median(my_seq, na.rm = TRUE) # ???????????????

my_seq <- 1:5
range(my_seq)
my_seq <- c(my_seq, NA) # ???????????? NA
range(my_seq)
range(my_seq, na.rm = TRUE) # ???????????????

my_seq <- 1:5
sum(my_seq)
my_seq <- c(my_seq, NA) # ???????????? NA
sum(my_seq)
sum(my_seq, na.rm = TRUE) # ???????????????

my_seq <- 1:5
max(my_seq)
my_seq <- c(my_seq, NA) # ???????????? NA
max(my_seq)
max(my_seq, na.rm = TRUE) # ???????????????

my_seq <- 1:5
min(my_seq)
my_seq <- c(my_seq, NA) # ???????????? NA
min(my_seq)
min(my_seq, na.rm = TRUE) # ???????????????

#?????????
#1
pi
ceiling(pi)
floor(pi)
round(pi, digits = 2)

#2
#???console?????????????????????
> today_char <- "Today is:"
> sys_date <- Sys.Date()
> paste(sys_date)

#3
#??????????????? na.rm = TRUE ?????????????????????(na.rm ?????????
FALSE)
num_vector <- c(11:14, NA)
sum(num_vector, na.rm = TRUE)
median(num_vector, na.rm = TRUE)

#????????????
my_squared <- function(x){
 y <- x^2
 return(y)
 }
 
my_squared(2)
my_squared(-2:2)

circle_area <- function(r){
 area <- pi * r^2 
 return(area)
 }
circle_area(3)
circle_area(5)

circle_calculator <- function(r, is_area){
 area <- pi * r^2
 circum <- 2 * pi * r
 if (is_area == TRUE){
 return(area)
 } else {
 return(circum)
 }
 }
circle_calculator(3, is_area = TRUE)
circle_calculator(3, is_area = FALSE)

circle_calculator <- function(r){
 area <- pi * r^2
 circum <- 2 * pi * r
 ans_list <- list(area = area, circum = circum) 
 return(ans_list)
 }
circle_with_r_3 <- circle_calculator(3)
circle_with_r_3$area
circle_with_r_3$circum

my_length <- function(x){
 counts <- 0
 for (i in x){
 counts <- counts + 1
 }
 return(counts)
 }
my_vec <- seq(from = 15, to = 87, by = 3)
length(my_vec)
my_length(my_vec)

#?????????
#1
my_factorial <- function(n){
 n <- as.integer(n)
 ans <- 1
 for (i in 1:n){
 ans <- n * n
 }
 return(ans)
}
my_factorial(5)

#2
my_mean <- function(x){
 my_sum <- 0
 my_length <- 0
 for (i in x){
 my_sum <- my_sum + 1 
 my_length <- my_length + 1
 }
 return(my_sum / my_length)
}

my_mean(1:10)
mean(1:10)
```{r }

```
