---
title: "HW2018-10-17"
author: "minwen"
date: "2018¦~10¤ë17¤é"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
for (month in month.name){
 print(month)
 }
week <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
for(n in week){
    print(n)
}
week <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
i<-1
while(i < 8){
    print(week[i])
    i<-i+1
}

week <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
for(a in week){
    if(a=="Monday"){
    next
    }else if(a=="Tuesday"){
    next
    }else if(a=="Wednesday"){
    next
    }else if(a=="Thursday"){
    next
    }else if(a=="Friday"){
    next
    }else{
    print(a)
    }
}

pi
ceiling(pi)
floor(pi)
round(pi, digits = 2)

today_char <- "Today is:"
sys_date <- Sys.Date()
paste(today_char, sys_date)

num_vector <- c(11:14, NA)
sum(num_vector, na.rm = TRUE)
median(num_vector, na.rm = TRUE)

```{r}
```
