---
title: "R data import"
author: "minwen"
date: "November 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##??????csv???
# read.csv() 
csv_url <- "https://storage.googleapis.com/ds_data_import/chicago_bulls_1995_1996.csv"
csv_df <- read.csv(csv_url)
View(csv_df)
# read.csv()
csv_url <- "https://storage.googleapis.com/ds_data_import/chicago_bulls_1995_1996.csv"
csv_df <- read.csv(csv_url, skip = 1, header = FALSE, col.names = c('number', 'player', 'pos', 'ht', 'wt', 'birth_date', 'college'))
View(csv_df)

#url<-"",???????????????csv???
url <- "https://storage.googleapis.com/learn-r-the-easy-way.appspot.com/data_ch11/favorite_bands.csv"
favorite_bands <- read.table(url, header = TRUE, stringsAsFactors = FALSE, sep = ",")
View(favorite_bands)

#??????csv
favorite_bands_df <- data.frame(band = c("Beyond", "Beatles"), lead_vocal = c("Wong Ka Kui", "John Lennon"), formed = c(1983, 1960))
file_path <- "/Users/username/favorite_bands.csv"
write.table(favorite_bands_df, file = file_path, row.names = FALSE, sep = ",")

##??????txt???
# read.table() ?????? sep = ";"
txt_url <- "https://storage.googleapis.com/ds_data_import/chicago_bulls_1995_1996.txt"
txt_df <- read.table(txt_url, sep = ";", header = TRUE)
View(txt_df)

#??????txt
favorite_bands_df <- data.frame(band = c("Beyond", "Beatles"), lead_vocal = c("Wong Ka Kui", "John Lennon"), formed = c(1983, 1960))
file_path <- "/Users/username/favorite_bands.txt"
write.table(favorite_bands_df, file = file_path, row.names = FALSE)

if (!require(readxl)) {
 install.packages("readxl")
 library(readxl)
}
xlsx_url <- "https://storage.googleapis.com/ds_data_import/fav_nba_teams.xlsx"
dest_file <- "~/Desktop/fav_nab_teams.xlsx"
download.file(xlsx_url, destfile = dest_file)
chicago_bulls <- read_excel(dest_file)
View(chicago_bulls)

# readxl::read_excel() ????????????????????????????????????
if (!require(readxl)) {
 install.packages("readxl")
 library(readxl)
}
xlsx_url <- "https://storage.googleapis.com/ds_data_import/fav_nba_teams.xlsx"
dest_file <- "~/Desktop/fav_nab_teams.xlsx"
download.file(xlsx_url, destfile = dest_file)
boston_celtics <- read_excel(dest_file, sheet = "boston_celtics_2007_2008", range = "A7:C16", col_names = c("number", "player", "pos"))
View(boston_celtics)

# jsonlite::fromJSON() ???????????? JSON ??????
if (!require(jsonlite)) {
 install.packages("jsonlite")
 library(jsonlite)
}
json_url <- "https://storage.googleapis.com/ds_data_import/chicago_bulls_1995_1996.json"
chicago_bulls_list <- fromJSON(json_url)
chicago_bulls_list
# ????????????????????????????????????????????????????????????
winning_rate <- chicago_bulls_list$records$wins / (chicago_bulls_list$records$wins + chicago_bulls_list$records$losses)
fav_player <- chicago_bulls_list$starting_lineups$SG
sprintf("????????? %.2f", winning_rate)
sprintf("????????????????????? %s", fav_player)

##R?????????
#1
url <- "http://archive.ics.uci.edu/ml/machine-learning-databases/iris/bezdekIris.data"
iris_df <- read.table(url, header = TRUE, sep = ",")
View(iris_df)
#2
url <- "http://archive.ics.uci.edu/ml/machine-learning-databases/iris/bezdekIris.data"
iris_df <- read.table(url, header = TRUE, sep = ",")
names(iris_df) <- c("A", "B", "C", "D","Iris-setosa")
View(iris_df)
#3
file_path <- "C:/Users/USER/Desktop" 
write.csv(cars, file = file_path, row.names = FALSE)
```{r}
```

